\documentclass[10pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[top=1.8cm, bottom=0.8cm, left=2.2cm, right=2.2cm]{geometry}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{parskip}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{titlesec}
\pagestyle{fancy}
\fancyhf{}
\rhead{\small SAAM Project --- Group AU}
\lhead{\small Sales Pitch}
\rfoot{\small\thepage}
\setlength{\parskip}{3.5pt}
\setlength{\parindent}{0pt}
\titleformat{\subsection}{\bfseries\normalsize}{}{0pt}{}[{\vspace{2pt}\hrule\vspace{4pt}}]
\titlespacing{\subsection}{0pt}{8pt}{0pt}
\begin{document}
\begin{center}
    {\LARGE \textbf{Decarbonise European Equities Without Giving Up the
    Benchmark}}\\[0.15cm]
    {\large A Practical, Rules-Based Decarbonisation Framework}\\[0.15cm]
    {\normalsize Group AU --- HEC Lausanne --- May 2026}
\end{center}
\vspace{0.08cm}
\rule{\linewidth}{1pt}
\vspace{-0.2cm}

Institutional investors face a clear challenge: reduce portfolio carbon
exposure while preserving the financial profile of a broad European equity
allocation. Our results suggest this trade-off can be managed more efficiently
than many investors expect. Using 12 years of out-of-sample data on 633
European equities, we find that a rules-based decarbonisation strategy can
deliver large carbon reductions at a limited observed performance cost.

\subsection{Two Practical Portfolio Solutions}
We tested two long-only, annually rebalanced strategies relative to the
European value-weighted benchmark:

\begin{enumerate}[leftmargin=*, itemsep=2pt, topsep=3pt]
    \item \textbf{50\% Carbon Cap} ($P^{vw}(0.5)$): a portfolio designed to
    stay as close as possible to the benchmark while cutting its carbon
    footprint by 50\% each year.
    \item \textbf{Net-Zero Glide Path} ($P^{vw}(NZ)$): a Paris-aligned
    strategy that reduces the carbon budget by 10\% per year from the 2013
    baseline, in the spirit of the EU Climate Transition Benchmark framework.
\end{enumerate}

\subsection{Headline Results}
\begin{table}[h]
\vspace{-2pt}
\centering
\begin{tabular}{lccc}
\toprule
Strategy & Geometric Return & Return Gap vs.\ Benchmark & Carbon Reduction \\
\midrule
Benchmark $P^{vw}$       & 7.16\% & ---      & ---             \\
50\% Cap $P^{vw}(0.5)$   & 6.78\% & $-$38 bp & $-$50\%         \\
Net-Zero $P^{vw}(NZ)$    & 6.84\% & $-$32 bp & $-$72\% by 2024 \\
\bottomrule
\end{tabular}
\end{table}
\vspace{-8pt}
\begin{center}
{\small\textit{Out-of-sample, January 2014 -- December 2025. Zero risk-free rate.}}
\end{center}

These results indicate that substantial decarbonisation was achievable in
our European sample at a modest observed cost in return terms. The Net-Zero
glide path was even slightly cheaper than the static 50\% cap, because the
benchmark itself decarbonised significantly over the period.

\subsection{Why the Strategy Works}
The carbon footprint of the benchmark is highly concentrated. In 2013, just
ten firms --- including Holcim, Rio Tinto, RWE and Enel --- accounted for
44\% of the benchmark's weighted-average carbon intensity. That concentration
means a portfolio manager does not need to rebuild the entire index to
decarbonise it: selective underweighting of a small group of high-intensity
names can already deliver large carbon savings.

A second factor in our sample is that the European benchmark's own carbon
footprint fell by 58\% between 2013 and 2024, even without any portfolio
intervention. That made a progressive Net-Zero constraint particularly
efficient over this period.

\subsection{Risks and Trade-offs}
We do not present this as a universal result. Three caveats matter:
\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=3pt]
    \item \textbf{Sample dependence.} These findings reflect European equities
    over 2014--2025 and may not carry over to other markets or periods.
    \item \textbf{Incomplete emissions coverage.} The analysis uses Scope 1
    and Scope 2 emissions only; Scope 3 remains excluded.
    \item \textbf{Implementation frictions.} Transaction costs, turnover and
    real-world trading constraints would need to be assessed before
    deployment.
\end{itemize}

\subsection{Recommendation}
For an investor seeking immediate and measurable decarbonisation, the
\textbf{50\% carbon-cap strategy} provides a clear, transparent solution with
limited deviation from benchmark performance.

For an investor seeking long-term regulatory alignment and a smoother
transition path, the \textbf{Net-Zero glide path} is the stronger choice. In
our sample, it delivered the deepest carbon reduction with a slightly smaller
observed return cost than the static cap.

Both approaches are rules-based, transparent, and offer a credible
implementation framework for a client objective centred on lowering financed
emissions while maintaining a recognisably benchmark-like European equity
allocation.

\vspace{0.3cm}
\rule{\linewidth}{1pt}
\begin{center}
{\small Arthur Pillet \quad Nathan Heimendinger Dreyfus \quad Marc Muller \quad Evan Dejean}\\
{\small HEC Lausanne --- Sustainability Aware Asset Management --- May 2026}
\end{center}
\end{document}
